\documentclass[11pt,a4paper,sans]{moderncv}

% Style
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[margin=1cm]{geometry}
\usepackage{lmodern}

% Personal Info
\firstname{George}
\familyname{Raafat}
\phone[mobile]{+20 1271601014}
\email{georgexraafat@gmail.com}
\address{Cairo, Egypt}{11687}{}
\social[linkedin]{georgeraafat}
\social[github]{George-Raafat}

\begin{document}

\makecvtitle

\vspace{-1.5em}

{\LARGE \textbf{Back-end Software Engineer}}

\vspace{-0.5em}
%------------------------------------------------------------------------------
\section{Summary}
Back-end engineer skilled in building secure APIs, optimizing databases, and delivering scalable, reliable software through testing, containerization, and collaborative development.

\vspace{-0.5em}
%------------------------------------------------------------------------------
\section{Education}
\cventry{10/2022 -- 06/2026}{B.Sc. in Computer Science}{Cairo University}{Faculty of Computers \& Artificial Intelligence}{}{
\begin{itemize}
  \item GPA: 3.8 (4th-year student)
\end{itemize}}

\vspace{-0.5em}
%------------------------------------------------------------------------------
\section{Experience}

\cventry{07/2025 -- 08/2025}{Back-end Development Intern}{Banque Misr}{Hybrid}{}{
\begin{itemize}
  \item Completed a 6-week back-end internship using Spring Boot and JWT for secure applications.
  \item Worked with MySQL and MongoDB for database integration and management.
  \item Implemented unit and integration tests to ensure code reliability.
  \item Gained hands-on experience with Docker for containerization and deployment.
  \item Practiced Git workflows and application preparation for production.
\end{itemize}}
\cventry{09/2024 -- 11/2024}{Back-end Developer}{NCI (via ALX Ventures)}{Remote}{}{
\textcolor{blue}{\href{https://savanna.alxafrica.com/certificates/h7mr659pEx}{View Certificate}}
\begin{itemize}
  \item Built and deployed a scalable API for an inventory management SaaS (Nest.js, MongoDB).
  \item Implemented multi-tenant database architecture to streamline client data management.
\end{itemize}}

\cventry{02/2023 -- 04/2024}{Software Engineering Intern}{ALX Africa}{Remote}{}{
\textcolor{blue}{\href{https://intranet.alxswe.com/certificates/en8H5ZG72p}{View Certificate}}
\begin{itemize}
  \item Completed 12-month intensive program specializing in back-end development.
  \item Developed full-stack web applications using Flask, Next.js, and React.
  \item Designed and optimized databases with MySQL and MongoDB (Prisma, SQLAlchemy).
  \item Practiced agile workflows, Linux development, Git, and test-driven coding.
\end{itemize}}

\vspace{-0.5em}
%------------------------------------------------------------------------------
\section{Projects}

\cventry{12/2024 -- 12/2024}{Learning Management System}{}{}{}{
\begin{itemize}
  \item Built a web platform for managing courses and assessments (Spring Boot, PostgreSQL).
  \item Designed normalized schemas and integrated Cloudinary for media management.
\end{itemize}}

\cventry{03/2024 -- 04/2024}{Doodles}{}{}{}{
\begin{itemize}
  \item Developed drawing-sharing web app (Next.js, React, Prisma, MongoDB, NextAuth).
  \item Implemented authentication, database optimization, and image storage with Cloudinary.
\end{itemize}}

\cventry{11/2023 -- 12/2023}{Sports Club Center}{}{}{}{
\begin{itemize}
  \item Built a RESTful API in Flask with SQLAlchemy/MySQL for sports club activity management.
  \item Delivered a console-based admin interface for database management.
\end{itemize}}

\vspace{-0.5em}
%------------------------------------------------------------------------------
\section{Skills}
\cvitem{Programming Languages}{C, C++, Python, Java, HTML, CSS, JavaScript/TypeScript}
\cvitem{Frameworks}{Flask, Django, Spring Boot, Nest.js, Next.js}
\cvitem{Databases}{MySQL, PostgreSQL, SQL Server, MongoDB}
\cvitem{Tools \& Technologies}{Git, Docker, Linux, Prisma}
\cvitem{Soft Skills}{Communication, Teamwork, Time Management, Attention to Detail}

\end{document}
